6.867 Problem Set 1

### 2015-12-10 Project/Latex/Paper.tex
[project] update some plots.

>>>>

We wanted to determine how our Naive Bayes implementation did compared to an off-the-shelf implementation of the same algorithm. In order to do so, we trained NLTK's multinomial Naive Bayes classifier on the same training data, and then evaluated the sentiment of 1,000 articles. A comparison of the two implementations is found below:
